### 2020-12-13 README.Rmd
change README

- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)

>>>>

- `capitals`: a list of capitals and capital transition for Correlates of War state system members
- `cow_ddy`: a full directed dyad-year data frame of Correlates of War state system members
- `cow_majors`: Correlates of War major powers data (version: 2016)
- `cow_states`: Correlates of War state system membership data (version: 2016)
- `gw_states`: Gleditsch-Ward independent state system data (version: 2017)
